---
title: "SFA extract features Deng et al 2014"
author: "Kushal K Dey"
date: "June 17, 2016"
output: 
  html_document:
    css: floating-toc.css
    toc: true
---
```{r}
library(knitr)
source("../R/SFA.ExtractTopFeatures.R")
```

## Loading Deng et al 2014 

```{r}
library(devtools)

read.data1 = function() {
  x = tempfile()
  download.file('https://cdn.rawgit.com/kkdey/singleCellRNASeqMouseDeng2014/master/data/Deng2014MouseEsc.rda', destfile=x, quiet=TRUE)
  z = get(load((x)))
  return(z)
}

Deng2014MouseESC <- read.data1()

deng.counts <- Biobase::exprs(Deng2014MouseESC)
deng.meta_data <- Biobase::pData(Deng2014MouseESC)
deng.gene_names <- rownames(deng.counts)

```

## Load the SFA input (sparse loadings: sqrt transformation)

```{r}
lambda_out <- read.table("../sfa_outputs/Deng2014PPS/sqrt_deng_counts_lambda.out")
f_out <- t(read.table("../sfa_outputs/Deng2014PPS/sqrt_deng_counts_F.out"))

indices_mat <- SFA.ExtractTopFeatures(f_out, top_features = 100, options="min")

top_gene_names <- t(apply(indices_mat, 1, function(x) return (deng.gene_names[x])));

```

## Factor Annotations 

### Factor 1 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[1,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_sqrt/gene_names_clus_",1,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 2 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[2,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_sqrt/gene_names_clus_",2,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 3 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[3,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_sqrt/gene_names_clus_",3,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 4 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[4,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_sqrt/gene_names_clus_",4,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 5 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[5,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_sqrt/gene_names_clus_",5,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 6 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[6,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_sqrt/gene_names_clus_",6,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 7 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[7,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_sqrt/gene_names_clus_",7,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 8 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[8,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_sqrt/gene_names_clus_",8,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 9 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[9,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_sqrt/gene_names_clus_",9,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 10 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[10,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_sqrt/gene_names_clus_",10,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```


## Load the SFA input (sparse loadings: voom transformation)

```{r}
lambda_out <- read.table("../sfa_outputs/Deng2014PPS/voom_deng_counts_lambda.out")
f_out <- t(read.table("../sfa_outputs/Deng2014PPS/voom_deng_counts_F.out"))

indices_mat <- SFA.ExtractTopFeatures(f_out, top_features = 100, options="min")

top_gene_names <- t(apply(indices_mat, 1, function(x) return (deng.gene_names[x])));

```

## Factor Annotations

### Factor 1 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[1,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_voom/gene_names_clus_",1,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 2 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[2,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_voom/gene_names_clus_",2,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 3 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[3,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_voom/gene_names_clus_",3,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 4 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[4,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_voom/gene_names_clus_",4,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 5 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[5,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_voom/gene_names_clus_",5,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 6 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[6,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_voom/gene_names_clus_",6,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 7 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[7,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_voom/gene_names_clus_",7,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 8 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[8,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_voom/gene_names_clus_",8,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 9 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[9,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_voom/gene_names_clus_",9,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 10 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[10,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_load_voom/gene_names_clus_",10,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

## Load the SFA input (sparse factors: sqrt transformation)

```{r}
lambda_out <- read.table("../sfa_outputs/Deng2014PPS/sqrt_deng_counts_transpose_lambda.out")
f_out <- read.table("../sfa_outputs/Deng2014PPS/sqrt_deng_counts_transpose_F.out")

indices_mat <- SFA.ExtractTopFeatures(lambda_out, top_features = 100, options="min")

top_gene_names <- t(apply(indices_mat, 1, function(x) return (deng.gene_names[x])));

```

## Factor Annotations

### Factor 1 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[1,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_sqrt/gene_names_clus_",1,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 2 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[2,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_sqrt/gene_names_clus_",2,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 3 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[3,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_sqrt/gene_names_clus_",3,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 4 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[4,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_sqrt/gene_names_clus_",4,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 5 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[5,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_sqrt/gene_names_clus_",5,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 6 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[6,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_sqrt/gene_names_clus_",6,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 7 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[7,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_sqrt/gene_names_clus_",7,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 8 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[8,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_sqrt/gene_names_clus_",8,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 9 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[9,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_sqrt/gene_names_clus_",9,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 10 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[10,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_sqrt/gene_names_clus_",10,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

## Load the SFA input (sparse factors: voom transformation)

```{r}
lambda_out <- read.table("../sfa_outputs/Deng2014PPS/voom_deng_counts_transpose_lambda.out")
f_out <- read.table("../sfa_outputs/Deng2014PPS/voom_deng_counts_transpose_F.out")

indices_mat <- SFA.ExtractTopFeatures(lambda_out, top_features = 100, options="min")

top_gene_names <- t(apply(indices_mat, 1, function(x) return (deng.gene_names[x])));

```

## Factor Annotations

### Factor 1 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[1,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_voom/gene_names_clus_",1,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 2 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[2,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_voom/gene_names_clus_",2,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 3 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[3,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_voom/gene_names_clus_",3,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 4 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[4,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_voom/gene_names_clus_",4,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 5 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[5,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_voom/gene_names_clus_",5,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 6 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[6,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_voom/gene_names_clus_",6,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 7 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[7,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_voom/gene_names_clus_",7,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 8 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[8,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_voom/gene_names_clus_",8,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 9 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[9,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_voom/gene_names_clus_",9,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 10 annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(top_gene_names[10,],  scopes="symbol", fields=c("name", "summary"), species="mouse");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/Deng2014_sparse_fac_voom/gene_names_clus_",10,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```
