---
title: 'Gene Annotations from SFA: GTEx'
author: "Kushal K Dey"
date: "June 18, 2016"
output: 
  html_document:
    css: floating-toc.css
    toc: true
---

```{r packages, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
library(maptpx)
library(qtlcharts)
library(data.table)
library(mygene)
library(CountClust)
library(knitr)
```

```{r}
library(knitr)
source("../R/SFA.ExtractTopFeatures.R")
source("../R/SFA.TopFeaturesPerFac.R")
```



We perform gene annotations from the GTEx SFA analysis.

## GTEx 2013 Factor analysis (sparse loadings: sqrt counts)

```{r}
lambda_out <- read.table("../sfa_outputs/GTEX2013/counts_sqrt_gtex/counts_sqrt_gtex_lambda.out");
f_out <- t(read.table("../sfa_outputs/GTEX2013/counts_sqrt_gtex/counts_sqrt_gtex_F.out"));

gene_names <- as.vector(as.matrix(read.table("../sfa_inputs/gene_names_GTEX_V6.txt")));
gene_names <- substring(gene_names,1,15);
xli  <-  gene_names;

#indices_mat <- SFA.TopFeaturesPerFac(f_out, top_features = 100)

indices_mat <- SFA.ExtractTopFeatures(f_out, top_features = 100,
                      options = "min",mult.annotate = TRUE)

gene_list <- do.call(rbind, lapply(1:dim(indices_mat)[1], function(x) gene_names[indices_mat[x,]]))

```

### SFA loadings plot


```{r}
samples_id <- read.table("../sfa_inputs/samples_id.txt");

tissue_labels <- vector("numeric", NROW(samples_id))
tissue_labels <- samples_id[ ,3]

tissue_levels <- unique(tissue_labels);


cumsum_val <- c(1,cumsum(as.numeric(table(tissue_labels))))
cumsum_low <- cumsum_val[1:(length(cumsum_val)-1)]
cumsum_high <- cumsum_val[2:(length(cumsum_val))];
cumsum_mean <- 0.5*(cumsum_low+cumsum_high)


for(k in 1:20){
png(paste0("../sfa_outputs/GTEX2013_transpose/sfa-figures/sqrt_counts_sparse_load_loadings/gtex_sfa_loadings_",k,".png"), width=4, height=4, units="in", res=600)
par(mar=c(6,3,1,1))
par(mar=c(10,3,2,2))
barplot(lambda_out[,k], axisnames=F,space=0,border=NA,
        main=paste0("SFA on gtex expression: loading:", k),
        las=1, cex.axis=0.3,cex.main=0.4,
        ylim=c(min(lambda_out[,k]),max(lambda_out[,k])))
axis(1,at=cumsum_mean,unique(tissue_labels),las=2, cex.axis=0.3);
abline(v=cumsum_high)
dev.off()
}

```

### Factor 1 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[1,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",1,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```


### Factor 2 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[2,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",2,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 3 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[3,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",3,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 4 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[4,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",4,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 5 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[5,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",5,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 6 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[6,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",6,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 7 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[7,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",7,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 8 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[8,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",8,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 9 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[9,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",9,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 10 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[10,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",10,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 11 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[11,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",11,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 12 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[12,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",12,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 13 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[13,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",13,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 14 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[14,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",14,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 15 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[15,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",15,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 16 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[16,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",16,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 17 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[17,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",17,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 18 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[18,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",18,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 19 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[19,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",19,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 20 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[20,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_sqrt/gene_names_clus_",20,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

## GTEx 2013 Factor analysis (sparse loadings: voom counts)

```{r}
lambda_out <- read.table("../sfa_outputs/GTEX2013/voom_gtex/voom_gtex_sfa_lambda.out");
f_out <- t(read.table("../sfa_outputs/GTEX2013/voom_gtex/voom_gtex_sfa_F.out"));

gene_names <- as.vector(as.matrix(read.table("../sfa_inputs/gene_names_GTEX_V6.txt")));
gene_names <- substring(gene_names,1,15);
xli  <-  gene_names;

indices_mat <- SFA.ExtractTopFeatures(f_out, top_features = 100,
                      options = "min",mult.annotate = TRUE)

gene_list <- do.call(rbind, lapply(1:dim(indices_mat)[1], function(x) gene_names[indices_mat[x,]]))

```

### SFA loadings plot


```{r}

samples_id <- read.table("../sfa_inputs/samples_id.txt");

tissue_labels <- vector("numeric", NROW(samples_id))
tissue_labels <- samples_id[ ,3]

tissue_levels <- unique(tissue_labels);


cumsum_val <- c(1,cumsum(as.numeric(table(tissue_labels))))
cumsum_low <- cumsum_val[1:(length(cumsum_val)-1)]
cumsum_high <- cumsum_val[2:(length(cumsum_val))];
cumsum_mean <- 0.5*(cumsum_low+cumsum_high)

for(k in 1:20){
png(paste0("../sfa_outputs/GTEX2013_transpose/sfa-figures/voom_sparse_load_loadings/gtex_sfa_loadings_",k,".png"), width=4, height=4, units="in", res=600)
par(mar=c(6,3,1,1))
par(mar=c(10,3,2,2))
barplot(lambda_out[,k], axisnames=F,space=0,border=NA,
        main=paste0("SFA on gtex expression: loading:", k),
        las=1, cex.axis=0.3,cex.main=0.4,
        ylim=c(min(lambda_out[,k]),max(lambda_out[,k])))
axis(1,at=cumsum_mean,unique(tissue_labels),las=2, cex.axis=0.3);
abline(v=cumsum_high)
dev.off()
}

```

### Factor 1 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[1,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",1,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 2 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[2,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",2,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 3 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[3,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",3,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 4 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[4,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",4,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 5 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[5,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",5,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 6 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[6,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",6,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 7 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[7,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",7,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 8 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[8,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",8,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 9 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[9,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",9,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 10 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[10,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",10,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 11 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[11,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",11,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 12 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[12,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",12,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 13 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[13,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",13,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 14 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[14,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",14,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 15 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[15,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",15,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 16 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[16,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",16,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 17 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[17,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",17,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 18 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[18,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",18,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 19 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[19,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",19,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 20 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[20,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_load_voom/gene_names_clus_",20,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```


Transpose the matrix to ensure sparse factors 

```{r echo=TRUE, eval=FALSE}

##  Voom counts transpose

#Expected complete Log likelihood at iteration 100: -8.18694e+07
#Marginal log likelihood at iteration 100: inf
#Residual variance at iteration 100: 1.72648
#Residual sum of squares at iteration 100: 6.53386e+07

##  Sqrt counts transpose

# Expected complete Log likelihood at iteration 100: -3.9495e+08
# Marginal log likelihood at iteration 100: -inf
# Residual variance at iteration 100: 638.648
# Residual sum of squares at iteration 100: 2.35575e+10

## counts transpose

```



## GTEx 2013 Factor analysis (sparse factors: sqrt counts)

```{r}
lambda_out <- read.table("../sfa_outputs/GTEX2013_transpose/sqrt_counts_gtex/gtex_sqrt_counts_transpose_lambda.out");
f_out <- read.table("../sfa_outputs/GTEX2013_transpose/sqrt_counts_gtex/gtex_sqrt_counts_transpose_F.out");

gene_names <- as.vector(as.matrix(read.table("../sfa_inputs/gene_names_GTEX_V6.txt")));
gene_names <- substring(gene_names,1,15);
xli  <-  gene_names;


indices_mat <- SFA.ExtractTopFeatures(lambda_out, top_features = 100, options = "min",mult.annotate = TRUE)


gene_list <- do.call(rbind, lapply(1:dim(indices_mat)[1], function(x) gene_names[indices_mat[x,]]))

```

### SFA loadings plot


```{r}

samples_id <- read.table("../sfa_inputs/samples_id.txt");

tissue_labels <- vector("numeric", NROW(samples_id))
tissue_labels <- samples_id[ ,3]

tissue_levels <- unique(tissue_labels);


cumsum_val <- c(1,cumsum(as.numeric(table(tissue_labels))))
cumsum_low <- cumsum_val[1:(length(cumsum_val)-1)]
cumsum_high <- cumsum_val[2:(length(cumsum_val))];
cumsum_mean <- 0.5*(cumsum_low+cumsum_high)

for(k in 1:20){
png(paste0("../sfa_outputs/GTEX2013_transpose/sfa-figures/sqrt_counts_sparse_fac_loadings/gtex_sfa_loadings_",k,".png"), width=4, height=4, units="in", res=600)
par(mar=c(6,3,1,1))
par(mar=c(10,3,2,2))
barplot(t(f_out)[,k], axisnames=F,space=0,border=NA,
        main=paste0("SFA on gtex expression: loading:", k),
        las=1, cex.axis=0.3,cex.main=0.4,
        ylim=c(min(f_out[k,]),max(f_out[k,])))
axis(1,at=cumsum_mean,unique(tissue_labels),las=2, cex.axis=0.3);
abline(v=cumsum_high)
dev.off()
}

```


### Factor 1 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[1,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",1,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 2 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[2,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",2,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 3 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[3,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",3,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 4 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[4,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",4,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 5 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[5,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",5,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 6 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[6,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",6,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 7 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[7,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",7,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 8 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[8,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",8,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 9 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[9,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",9,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 10 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[10,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",10,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 11 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[11,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",11,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 12 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[12,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",12,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 13 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[13,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",13,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 14 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[14,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",14,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 15 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[15,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",15,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 16 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[16,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",16,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 17 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[17,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",17,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 18 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[18,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",18,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 19 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[19,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",19,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 20 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[20,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_sqrt/gene_names_clus_",20,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

## GTEx 2013 Factor analysis (sparse factors: voom counts)

```{r}
lambda_out <- read.table("../sfa_outputs/GTEX2013_transpose/voom_gtex/gtex_voom_transpose_lambda.out");
f_out <- read.table("../sfa_outputs/GTEX2013_transpose/voom_gtex/gtex_voom_transpose_F.out");

gene_names <- as.vector(as.matrix(read.table("../sfa_inputs/gene_names_GTEX_V6.txt")));
gene_names <- substring(gene_names,1,15);
xli  <-  gene_names;

indices_mat <- SFA.ExtractTopFeatures(lambda_out, top_features = 100, options = "min",mult.annotate = TRUE)


gene_list <- do.call(rbind, lapply(1:dim(indices_mat)[1], function(x) gene_names[indices_mat[x,]]))

```

### SFA loadings plot


```{r}
samples_id <- read.table("../sfa_inputs/samples_id.txt");

tissue_labels <- vector("numeric", NROW(samples_id))
tissue_labels <- samples_id[ ,3]

tissue_levels <- unique(tissue_labels);


cumsum_val <- c(1,cumsum(as.numeric(table(tissue_labels))))
cumsum_low <- cumsum_val[1:(length(cumsum_val)-1)]
cumsum_high <- cumsum_val[2:(length(cumsum_val))];
cumsum_mean <- 0.5*(cumsum_low+cumsum_high)

for(k in 1:20){
png(paste0("../sfa_outputs/GTEX2013_transpose/sfa-figures/voom_sparse_fac_loadings/gtex_sfa_loadings_",k,".png"), width=4, height=4, units="in", res=600)
par(mar=c(6,3,1,1))
par(mar=c(10,3,2,2))
barplot(t(f_out)[,k], axisnames=F,space=0,border=NA,
        main=paste0("SFA on gtex expression: loading:", k),
        las=1, cex.axis=0.3,cex.main=0.4,
        ylim=c(min(f_out[k,]),max(f_out[k,])))
axis(1,at=cumsum_mean,unique(tissue_labels),las=2, cex.axis=0.3);
abline(v=cumsum_high)
dev.off()
}

```


### Factor 1 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[1,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",1,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 2 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[2,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",2,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 3 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[3,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",3,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 4 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[4,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",4,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 5 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[5,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",5,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 6 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[6,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",6,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 7 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[7,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",7,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 8 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[8,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",8,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 9 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[9,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",9,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 10 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[10,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",10,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 11 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[11,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",11,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 12 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[12,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",12,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 13 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[13,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",13,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 14 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[14,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",14,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 15 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[15,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",15,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 16 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[16,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",16,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 17 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[17,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",17,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 18 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[18,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",18,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 19 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[19,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",19,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```

### Factor 20 Annotations

```{r echo=TRUE, eval=TRUE}
out <- mygene::queryMany(gene_list[20,],  scopes="ensembl.gene", fields=c("name", "summary", "symbol"), species="human");
kable(as.data.frame(out))
write.table(as.factor(out$query), paste0("../utilities/GTEX2013_sparse_fac_voom/gene_names_clus_",20,".txt"), col.names = FALSE,
            row.names=FALSE, quote=FALSE);
```


